### 2014-05-14 Paper1/paper1.tex
Old version of latex blows...

\section*{Discussion}

>>>>

\section*{Discussion}
We sought to determine the plausibility and robustness of an algorithm that determines a person’s intent of a motion, even if there disturbances. Sensitivity analysis on synthetic data revealed that the method was plausible and response to parameter variations was more robust than human reaching, but significant misestimation could occur if the stiffness was inaccurately modeled. Examination of intended trajectories from force pulse-disturbed human reaching confirmed that these intentions remained statistically indistinguishable from undisturbed reaching for ~100ms following the onset of disturbance. This test provides a method for testing and potentially falsifying our extraction. Differences after this point could be attributed to many factors including unmodeled reflexes, changes in arm stiffness, or genuine change in movement intent. In the context of the sensitivity analysis, it appears most likely that this primarily represents a change in intent and thus a first look at how intent changes when faced with a force disturbance.

$\lambda$ models seek to explain reaching intent as the muscles’ equilibrium trajectory. By deriving the technique in a general form, we discovered that our $x_d$ can be used to determine the muscle equilibrium of a $\lambda$ model and that they are only equivalent when $x_d$ is not changing. Even as this rejects a major claim of those modeling approaches, it explains a key experimental underpinning: Bizzi’s et al.’s \cite{bizzi1984posture} discovery of a “virtual trajectory” in deafferented monkeys with a moving equilibrium point that progressed smoothly from the initial to final positions. Even if the muscle equilibrium jumped abruptly, this would be insufficient to move the intended trajectory abruptly due to the presence of a virtual mass.

Not only is intent slow to change, it does not necessarily change due to disturbance. While this work does not examine this directly, our observations are more compatible with intermittent control (or even submovements) than with continuous optimal feedback control. In classic optimal control, the system is always updating the intent in response to errors \cite{todorov2002optimal}. Our results suggest a latent response consistent with sensory feedback latencies \cite{pruszynski2012optimal}. Interestingly, our data disturbances that come later in the movement appeared to not dramatically affect the intent (Figure 3, lower plot), suggesting that people may stubbornly “stick to their guns” when they know that the stiffness and damping characteristics will provide enough restoring torque to arrive at the target. In other words, response latencies may be  dependent on the time of the disturbance in the movement. Another explanation is that control is intermittent \cite{gawthrop2011intermittent}. It remains to be seen if and how change in intent might be triggered.

This study might have large dividends in the study of error augmentation, which has demonstrated the capacity to increase and speed up learning in healthy patients \cite{patton2004robot} and following stroke \cite{patton2006evaluation}. This relies on dictating the direction of reach. By instead scaling the magnitude of the difference between the desired and realized trajectory, error augmentation during undirected reaching and exploration becomes possible. This permits both error reduction and error magnification. As demonstrated by the success of the challenge-point framework \cite{guadagnoli2004challenge}, dynamic variation of augmentation as task learning progresses can be beneficial. With this extraction, error can be measured and augmented in real time even without an explicit task, potentially enabling wider utility.
While derivation and validation of intent determination was somewhat complicated, the outcome is a single filter that converts force and motion information into an estimate of intention. This filter incorporates the inversion of estimates of the actual human controller into the computation. While a large number of filters have already been proposed, we believe this to be a unique tool to be added to the arsenal of analytical methods for exploring human motor control. It has immediate applications to motor learning, neurorehabilitation, and any field interested in human-machine interaction.  
The ability of such a filter to produce intended trajectories from force-disturbed movements allows for hypothesis testing that previously was not available. It is important to reiterate that because the human arm’s mass is almost always invertible, this approach can take \textbf{any} “candidate model” of human control and create a filter that estimates the intended trajectory. By using tests such as the straight line reaching test employed in this paper, one can evaluate which candidate produces the most plausible intended trajectory, supporting one model over another.  Instead of comparing two generative models to see which better approximates movement, it is now possible to perform element-by-element fitting. Mid-movement replanning is now falsifiable: do intended trajectories from disturbed motions differ from undisturbed motions? Similarly, claims of composition of desired trajectories by submovements should now be directly testable. Finally, optimal feedback models can now gain direct access to an intended trajectory to better understand and fit their cost function.

Nevertheless, there are some drawbacks and limitations to these methods.  One limiting requirement of this method is that accurate interface force (within a few tenths of a newton) is needed. Such instrumentation is available, but must be used with great care in order to preserve the accuracy of the estimate. Our sensitivity analysis on synthetic data revealed that slight error can lead to a trajectory that accumulates a drift due to bias caused by the force term. More importantly, while modern force sensors can be highly accurate with very high signal to noise ratios, they tend to drift over time, leading to error that can grow if the device is not periodically tared. Our empirical approach used several methods to mitigate these effects, and hence the errors became small. It remains to be seen if there are methods to reduce the errors from force error, or better to eliminate their need altogether.

Similarly, because our intent extraction approach involves integration, it  can be “re-zeroed” at any point in time to improve accuracy, provided new initial condition can be obtained. Our work in this study dealt with targeted point-to-point motions, and hence assumed that each motion’s initial position (prior to any motion) was equal to the initial intended position. In continuous motion tasks and other applications, it may be possible to obtain an indication from the operator to know that they are precisely where they intend to be at some moment in the activity, refining subsequent estimates.

This study did not examine all disturbances. Although we have found and validated a potentially powerful tool for examining human intention as it changes (or fails to) in response to disturbance, other disturbances. Even as we demonstrated the power of this tool, we couldn’t examine all force disturbances. Impulses and Gaussian noise have convenient spectral properties that provide some generality to this claim, but the arm model examined here is not a linear, time-invariant system. The eigenfunctions of this nonlinear system are not known and it is unclear which force disturbances might best expose critical vulnerabilities.

The approximation of stiffness appears to be the most critical factor in accuracy in estimating intent. While serious trial-to-trial stiffness misestimation is unlikely, co-contraction in response to disturbance might plausibly double stiffness mid-reach. Even as the model is insensitive to normal variations, halving or doubling this parameter due to contraction is plausible and has significant impact on accuracy. The limitations are readily overcome by performing this sensitivity analysis on each force environment of interest and taking measures to detect co-contraction where or when it occurs.

Our simple linear scaling of Burdet et al.'s stiffness model \cite{burdet2006stability} may not be all that is needed. More accurate approaches would provide us with too many free parameters through which to determine the outcome of the eventual extraction. Even scaling the constant and torque-dependent stiffness matrixes separately would enable rotation of the extracted trajectory. Our results point to the possibility of the impedance changing during motion, perhaps also as a function of time. The system was also shown to be sensitive to uncertainties in impedance. While this may be perceived as a shortcoming, switching from a state-varying impedance to ongoing time-varying determination of impedance may overcome these issues.
[summary and take home; Hypothesize /speculate what data suggest, are there new questions.  What contributions did this paper make? 
In any case, the general intent extraction approach presented here reveals the conditions needed to solve for the moving intent in an arbitrary dynamic process. Moreover, the plant model does not need to be explicitly formulated. Dynamic models that strive to understand intent are wide ranging, and can include mathematical models that range in application from national security to athletic performance. The plant (such as the actions of a crowd in a crowded square or the motions of the opposing team) may be too complex to model with simple linear transformations as we present above. However, by substituting some approximation or lookup table of input-outcome pairs, it is possible to determine in a variety of applications to obtain the intent, even when disturbed. It is not necessarily to allow a bomb to explode or the opposing team to be victorious to understand their plan behind the action.
